Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber}}

### 2018-02-20 Paper.tex
Fixing bracing

The normal halting function $H$ is defined:
\begin{equation}
H(\boldsymbol{\mu}, I) \equiv \begin{cases}
H_{\text{\tiny RETURN}}(\boldsymbol{\mu}) & \text{if} \quad w \in \{\text{\small \hyperlink{RETURN}{RETURN}}, \text{\small REVERT}\} \\
() & \text{if} \quad w \in \{ \text{\small {\hyperlink{stop}{STOP}}}, \text{\small \hyperlink{selfdestruct}{SELFDESTRUCT}}} \} \\
\varnothing & \text{otherwise}
\end{cases}
\end{equation}

>>>>

The normal halting function $H$ is defined:
\begin{equation}
H(\boldsymbol{\mu}, I) \equiv \begin{cases}
H_{\text{\tiny RETURN}}(\boldsymbol{\mu}) & \text{if} \quad w \in \{\text{\small \hyperlink{RETURN}{RETURN}}, \text{\small REVERT}\} \\
() & \text{if} \quad w \in \{ \text{\small \hyperlink{stop}{STOP}}}, \text{\small \hyperlink{selfdestruct}{SELFDESTRUCT}}\} \\
\varnothing & \text{otherwise}
\end{cases}
\end{equation}
